On the dynamic assessment of the Local-Maximum Entropy Material Point Method through an Explicit Predictor-Corrector Scheme

### 2020-10-05 Revisiones/PNA_MMP_Responses to the reviewers.tex

Of course, the employment of the \textit{max-ent} approximants is not free of difficulties. Some requirements such as the need for a convex domain, as well as those derived from its calculation (the determination of the Lagrange Multipliers, specially at the boundaries, or the obtainment of the minimizer of the logarithmic function), make the usage of it a challenging tool. However, the results depicted in this manuscript will strengthen the motivation of its employment in order to mitigate typical MPM problems such as cell-crossing, stress instabilities and the use of unstructured mesh.

Concerning the first issue mentioned by the reviewer, the special case of non-convex domains was discussed by Arroyo \& Ortiz~\cite{Arroyo2006}. Some of the solutions proposed by the aforementioned authors are : the possibility of replacing the Euclidean distance $\lVert  x - x_a  \rVert$ in the definition of the shape functions by the length of the shortest path contained within the domain connecting $x$ and $x_a$. Or the decomposition of the non-convex domain into convex sub-domains.  This topic has also been extensively studied in the context of MLS-based meshfree methods, for instance visibility, diffraction, and constrained path criteria. These methods are directly applicable to local \textit{max-ent} approximation.

\item \textit{Does the use of max-ent solve the problem of imposing Dirichlet boundary conditions in the MPM?}\\

Unfortunately, local \textit{max-ent} approximation technique only provides an efficient tool to transfer information from particles to nodes and vice versa. Hence, the difficulties of imposing Dirichlet boundary conditions (DBC) in the MPM persists since they are a direct consequence of discretising the continuum with material points instead of nodes, where traditionally DBC are imposed. However, any available technique employed to overcome this situation in the standard MPM can be translated to the \textit{max-ent} one thanks to the Kronecker-Delta property inherent to it \cite{Arroyo2006}. See for instance the work of Cortis {\it et al.} (2018) \cite{Cortis_et_al_2017_IJNME} as example of how DBC can be imposed in the MPM.

@@

These interesting publications will be added to the state of art of the revised manuscript. In the humble opinion of the authors, the XPIC approach is dedicated to mitigate the null space error produced during the transfer of information between particles and nodes. Therefore, it is related to the spatial discretisation instead of the temporal one. Meanwhile, the algorithm introduced in this research proposes the stabilisation within the adaptation of the predictor-corrector algorithm, which has been used traditionally in FEM to deal with fast dynamics. To the author\textquotesingle s knowledge, this is the first attempt to adapt the  traditional predictor-corrector scheme for the MPM framework.

\end{enumerate}

 \textit{The numerical examples are not impressive when the message of the paper is that this is good for fast dynamics problems. Compare to papers such as Ma et al. (2009) IJ Impact Engineering}\\

In the authors' opinion, the provided results are capable to highlight the capabilities of the LME-MPM-NPC proposed in the present work. It is important to remark the extension of this research: in order to isolate the strength of the proposed methodology, covering spatial and time discretization, only linear elastic problems are assessed.

### 2020-11-09 Revisiones/PNA_MMP_Responses to the reviewers.tex

These interesting publications will be added to the state of art of the revised manuscript. In the humble opinion of the authors, the XPIC approach is dedicated to mitigate the null space error produced during the transfer of information between particles and nodes. Therefore, it is related to the spatial discretisation instead of the temporal one. Meanwhile, the algorithm introduced in this research proposes the stabilisation within the adaptation of the predictor-corrector algorithm, which has been used traditionally in FEM to deal with fast dynamics. To the author\textquotesingle s knowledge, this is the first attempt to adapt the  traditional predictor-corrector scheme for the MPM framework.

\end{enumerate}

 \textit{The numerical examples are not impressive when the message of the paper is that this is good for fast dynamics problems. Compare to papers such as Ma et al. (2009) IJ Impact Engineering}\\

\sout{Contrary to the reviewer\textquotesingle s opinion,} In the authors' opinion, the provided results are capable to highlight the \sout{strong} capabilities of the \acrshort{LME-}MPM-NPC proposed in the present work. It is important to remark the extension of this research: in order to isolate the strength of the proposed methodology, covering spatial and time discretization, only linear elastic problems are assessed.
